---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tibblizer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/tibblizer)](https://CRAN.R-project.org/package=tibblizer)
<!-- badges: end -->

The goal of tibblizer is to make it easier to support tibbles in functions that are not currently designed to support them.

## Installation

You can install the released version of tibblizer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("tibblizer")
```

## Example

The `stats::reshape()` function assumes that `x[i, j]` returns a vector if `j` refers to a single columns.
Tibbles never drop dimensions and always return a data frame.
This results in a weird behavior of the reshape function:

```{r example-bad, error = TRUE}
N <- 3
M <- 2

tbl <- tibble::tibble(
  g = gl(N, M),
  time = rep(seq_len(M), N),
  variable = rnorm(M * N)
)

# Current behavior:
reshape(
  tbl, v.names = "variable",
  idvar = "g", timevar = "time", direction = "wide"
)

# Expected result:
reshape(
  as.data.frame(tbl), v.names = "variable",
  idvar = "g", timevar = "time", direction = "wide"
)
```

tibblizer to the rescue:
Use `tbl_()` to create a tibble-friendly version of the `reshape()` function:

```{r example-good, error = TRUE}
library(tibblizer)

reshape <- tbl_(reshape)

reshape(
  tbl, v.names = "variable",
  idvar = "g", timevar = "time", direction = "wide"
)
```

---

Please note that the 'tibblizer' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
[Copied to clipboard]
